Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-10 paper/structureScene.tex
align axes for Fig 2 on log compression

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design.
It appears empirically that their distribution is skewed towards the right, which means that the tail towards greater values is longer than the tail towards lower values.
However, skewness can be reduced by applying to all coefficients a pointwise concave transformation, \eg logarithmic.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.
\vl{Qu'en penses-tu ML ?}
\ml{tres bien, mettre les deux distributions de couleurs differentes}

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{feature_histogram.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{feature_histogram_logcompressed.png}}
\end{picture}
\caption{
\label{fig:histograms}
\vl{we should discuss color schemes and axis labels}}
\end{center}
\end{figure}

>>>>

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design.
It appears empirically that their distribution is skewed towards the right, which means that the tail towards greater values is longer than the tail towards lower values.
However, skewness can be reduced by applying to all coefficients a pointwise concave transformation, \eg logarithmic.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node[anchor=south west,inner sep=0] at (-0.01, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
\node (histlabel1) at (3, 0.01) {$\mathbf{S}\boldsymbol{x}$};
\draw[-{Latex[length=2mm]}] (0.05, 0.01) -- (histlabel1);
\draw[-{Latex[length=2mm]}] (0.05, 0.01) -- (0.05, 2.5);
\node at (1.5, -0.25) {(a)};
\node (histlabel2) at (8, 0.01) {$\log \mathbf{S}\boldsymbol{x}$};
\node[anchor=south west,inner sep=0] at (4, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
\draw[-{Latex[length=2mm]}] (3.8, 0.01) -- (histlabel2);
\draw[-{Latex[length=2mm]}] (5, 0.01) -- (5, 2.5);
\node at (6, -0.25) {(b)};
\end{tikzpicture}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}
